### 2020-09-14 paper/definitions.tex
Plots and appendix
List near cleaners algo

An edge $\{x, y\}$ is said to \emph{join}, or be between vertices $x$ and $y$ and is denoted by $xy$. Thus $xy$ and $yx$ mean the same edge (all our graphs are \emph{undirected}). If $xy \in E(G)$ then $x$ and $y$ are adjacent, connected or neighboring. By $N(x)$ we will denote the \emph{neighborhood} of $x$, that is all vertices $y$ such that $xy$ is an edge. If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.

@@

\TODO{Defs below to ch. 1}

>>>>

An edge $\{x, y\}$ is said to \emph{join}, or be between vertices $x$ and $y$ and is denoted by $xy$. Thus $xy$ and $yx$ mean the same edge (all our graphs are \emph{undirected}). If $xy \in E(G)$ then $x$ and $y$ are adjacent, connected or neighboring. By $N(x)$ we will denote the \emph{neighborhood} of $x$, that is all vertices $y$ such that $xy$ is an edge. Similarly, for $X \subseteq V(G)$, by $N(X)$ we will denote the neighborhood of $X$, that is all vertices of $v \in V(G) \setminus X$, so that there is a $x \in X$, that $xv$ is an edge in $G$. If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.

@@

\begin{defn}[line graph]
  The \emph{line graph} of a graph $G = (V, E)$ is the graph $L(G)$ with vertex set equal $E$, where $e, h \in E$ are adjacent in $L(G)$ if and only if they share an end in $G$.
\end{defn}

### 2020-09-14 paper/perfectGraphs.tex
List near cleaners algo

The notion of perfect graphs was first introduced by Berge in 1961 \cite{CB61} and it indeed captures some of the idea of graph being ''simple'' -- in all perfect graphs the coloring problem, maximum (weighted) clique problem, and maximum (weighted) independent set problem can be solved in polynomial time \cite{grotschel1993}. Other classical NP-complete problems are still NP-complete in perfect graphs e.g. Hamiltonian path \cite{Mller1996}, maximum cut problem \cite{Bodlaender1994} or dominating set problem \cite{Dewdney81}. \todo{all theese citations are about subclasses e.g. biparite graphs. Should we mention some subclasses?}

@@

This theorem is a consequence of a stronger result proven by Lovász:
\begin{theorem}
	\label{thm:omegaalpha}
	A graph $G$ is perfect if and only if for every induced subgraph $H$, the number of vertices of $H$ is at most $\alpha(H)\omega(H)$. \todo{proof!}
\end{theorem}

@@

@@

	\noindent Output: $O(|V|^5)$ subsets of $V(G)$, such that if $C$ is an amenable hole in $G$, then one of the subsets is a near-cleaner for $C$.
\end{alg}
\begin{algtext2}
	We will call a triple $(a, b, c)$ of vertices \emph{relevant} if $a \neq b$ (but possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.

	Given a relevant triple $(a, b, c)$ we can compute the following:
	\begin{itemize}
		\item $r(a,b,c) \leftarrow$~the cardinality of the largest anticomponent of $N(a, b)$, that contains a nonneibhbor of $c$, or 0, if $c$ is $N(a, b)$-complete.
		\item $Y(a,b,c) \leftarrow$~the union of all anticomponents of $N(a, b)$ that have cardinality strictly greater than $r(a, b, c)$.
		\item $W(a, b, c) \leftarrow$~the anticomponent of $N(a,b) \cup \{c\}$ that contains $c$.
		\item $Z(a, b, c) \leftarrow$~the set of all $Y(a, b, c) \cup W(a,b,c)$-complete vertices.
		\item $X(a, b, c) \leftarrow$~$Y(a,b,c) \cup Z(a,b,c)$.
	\end{itemize}

	For every two adjacent vertices $u, v$ compute the set $N(u, v)$ and list all such sets.
	For each relevant triple $(a,b,c)$ compute the set $X(a,b,c)$ and list all such sets.

	Output all subsets of $V(G)$ that are the union of a set from the first list and a set from the second list.
\end{algtext2}

@@

	For all $y_1 \in V(G)\setminus X$ and all 3-vertex paths $x_1-x_2-x_3$ of $G\setminus y_1$ we check the following:
	\begin{itemize}
		\item $R(x_1, y_1), R(x_2, y_2)$ both exist -- define $y_2$ as the neighbor of $y_1$ in $R(x_2, y_1)$.
		\item $r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2)$ ($=n$ say) 
		\item $r(x_3, y_1), r(x_3, y_2) \geq n$
	\end{itemize}
	\TODO{moze raczej $min(r(x_3, y_1), r(x_3, y_2)) = r(x_2, y_1) = r(x_1, y_2) = r(x_1, y_1) + 1$?}

>>>>

The notion of perfect graphs was first introduced by Berge in 1961 \cite{CB61} and it indeed captures some of the idea of graph being ''simple'' -- in all perfect graphs the coloring problem, maximum (weighted) clique problem, and maximum (weighted) independent set problem can be solved in polynomial time \cite{grotschel1993}. Other classical NP-complete problems are still NP-complete in perfect graphs e.g. Hamiltonian path \cite{Mller1996}, maximum cut problem \cite{Bodlaender1994} or dominating set problem \cite{Dewdney81}. There are many subclasses of perfect graphs, we take a look and benchmark our implementations on some of them in \Cref{sec:experiments}

@@

This theorem is a consequence of a stronger result proven by Lovász:
\begin{theorem}[\cite{LL72}, Claim 1 of \cite{GC03}]
	\label{thm:omegaalpha}
	A graph $G$ is perfect if and only if for every induced subgraph $H$, the number of vertices of $H$ is at most $\alpha(H)\omega(H)$.
\end{theorem}
\todo{proof? min. 1 page}
% \begin{proof}
% 	First assume that $G$ is perfect -- for every induced subgraph $H$, $\omega(G) = \chi(H)$. Since the number of vertices of $H$ is at most $\alpha(H)\chi(H)$, the claim follows.

% 	The proof of the converse we show is due to Gasparyan \cite{Gasparian1996}. Assume that $G$ is not perfect. Let $H$ be a minimally imperfect subgraph of $G$ and let $n$ be the number of vertices of $H$. Let $\alpha = \alpha(H), \omega = \omega(H)$.

% 	Then, because $H$ is \emph{minimally} imperfect, it satisfies:
% 	\begin{itemize}
% 		\item $\omega = \chi(H \setminus v)$, for every $v \in H(V)$,
% 		\item $\omega = \omega(H \setminus S)$, for every stable set $S \subseteq V(H)$. 
% 	\end{itemize}

% 	Let $A_0$ be a maximal stable set of $H$. Then $|A_0| = \alpha$ and for each $s \in A_0$ fix an $\omega$-coloring of the graph $H \setminus s$.
% \end{proof}

@@

\begin{defn}[relevant triple]
	Given a graph $G$, a triple $(a, b, c)$ of vertices is called \emph{relevant} if $a \neq b$ (but possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.
\end{defn}

@@

	\noindent Output: $O(|V|^5)$ subsets of $V(G)$, such that if $C$ is an amenable hole in $G$, then one of the subsets is a near-cleaner for $C$.
\end{alg}

\begin{algorithmic}[1]
	\mProcedure{List-Possible-Near-Cleaners}{$G$}
	\ls $X \gets \emptyset$
	\mForEach{relevant triple $(a, b, c)$}
		\ls $A \gets$ anticomponents of $N(\{a, b\})$
		\mIf{$c$ is $N(\{a, b\})$-complete}
			\ls $r \gets 0$
		\mElse
			\ls $r \gets$ the cardinality of the largest set of $A$ that contains 
			\lsx a nonneibhbor of $c$ 
		\mEndIf
		\ls $Y \gets \emptyset$ 
		\mForEach{$A_i \in A$}
			\mIf{$|V(A_i)| > r$}
				\ls $Y \gets Y \cup A_i$
			\mEndIf
			\mIf{$c \in A_i$}
				\ls $W \gets A_i$
			\mEndIf
		\mEndFor
		\ls $Z \gets$ the set of all $Y \cup W$-complete vertices
		\ls $X \gets X \cup (Y \cup Z)$ 
	\mEndFor
	\ls $N \gets \emptyset$
	\mForEach{edge $uv \in E(G)$}
		\ls $N \gets N \cup N(\{u, v\})$
	\mEndFor
	\ls $R \gets \emptyset$
	\mForEach{$X_i \in X$}
		\mForEach{$N_j \in N$}
			\ls $R \gets R \cup (X_i \cup N_j)$
		\mEndFor
	\mEndFor
	\ls \RETURN $R$
	\mEndProcedure
\end{algorithmic}

@@

	For all $y_1 \in V(G)\setminus X$ and all 3-vertex paths $x_1-x_2-x_3$ of $G\setminus y_1$ we check the following:
	\begin{itemize}
		\item $R(x_1, y_1), R(x_2, y_2)$ both exist -- define $y_2$ as the neighbor of $y_1$ in $R(x_2, y_1)$.
		\item $r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2) = min(r(x_3, y_1), r(x_3, y_2))$ 
	\end{itemize}
